Argennon: A Scalable Smart Contract Platform

### 2022-04-20 tex/A.tex
Clarify resource management
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

\begin{document}
    \maketitle
    \begin{abstract}
        Argennon is a cloud based blockchain and smart
        contract platform which tries to solve shortcomings of existing platforms. The Argennon blockchain uses a hybrid
        proof of stake (POS) consensus protocol, which is based on participation of every Argennon user.

>>>>

\begin{document}
    \maketitle
    \begin{abstract}
        Argennon is a cloud based blockchain and smart
        contract platform which tries to solve shortcomings of existing platforms. The Argennon blockchain uses a hybrid
        proof of stake (HPoS) consensus protocol, which is based on participation of every Argennon user. This hybrid
        protocol is able to combine the benefits of a centralized and a decentralized system.

### 2022-04-20 tex/sections/avm.tex
Clarify resource management
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The AscEE has two type of execution sessions: \emph{optimistic} and \emph{monitored}. Resource usage of an optimistic
session is always measured per session and default pre-defined resource caps are used. On the other hand, for a
monitored session, resources that can not be measured precisely are measured per application call and their caps are
determined per application call by the external HTTP request (i.e.\ transaction). In Argennon, the
type of execution session for each transaction is decided by the block proposer.

>>>>

The AscEE has two type of execution sessions: \emph{optimistic} and \emph{monitored}. Resource usage of an optimistic
session is always measured per session and default pre-defined resource caps are used. On the other hand, for a
monitored session, resources that can not be measured precisely are measured per application call and their caps are
determined per application call by the external HTTP request (i.e.\ transaction). The block proposer decides the
type of the execution session for each transaction.

In most consensus protocols, we can assume that the block proposer has enough incentive to filter out transactions
that spam run-time resources. Here by a run-time resource, we refer to a resource that at run-time, a limited amount
of it is available, but its surplus can not be stored for later use. Execution time and local memory are
examples of a run-time resource but permanent storage is not a run-time resource.

If a proposed block contains many transactions which need a lot of run-time resources, validators would not
be able to validate all transactions in a timely manner. Consequently, they may decide to reject the block or if they
spend enough resources, the confirmation of that block could take more time than usual. Longer block time is not
favoured by block proposers, because it means less throughput of the system which usually means less overall rewards
for them. In Argennon the management of run-time resources, is left to the block proposer.
